### 2021-03-05 paper3/appendix.tex
Use include instead of import
This has the advantage that I can compile one chapter at a time.

% \subsection{Why not use a fair clustering method?}
% Current fair clustering methods \citep{chierichetti2017fair, backurs2019scalable, huang2019coresets} cluster based on the protected attribute and thus are not applicable to our setting in which the deployment set is unlabeled and the training set is incomplete with respect to $s$.

% \begin{figure*}[t]
% \centering
% \includegraphics[width=0.6\textwidth,page=2]{figures/ideal.pdf}
% \caption{Overview of the zero-shot stratification problem. Training dataset (pairs of input data $x$ and class label $y$) will only contain data points that are labeled ``yes'' by the decision policy. This systematic bias might result in a subgroup(s) to have zero labeled data (in the example above, ``married'' subgroup has zero labeled data). The subgrouping information $s$ is unavailable/unlabeled at deployment time, and is only partially labeled at train time.}
% \label{fig:censoring}
% \end{figure*}

\section{Appendix}\label{sec:zsf-appendix}
\subsection{Results for Adult Income}\label{sec:adult-results}
\begin{figure*}[p]
    \centering
    \includegraphics[width=\columnwidth]{figures/adult_partial_acc.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_partial_prr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_partial_tprr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_partial_tnrr.pdf}
    \caption{%
    Results for the Adult Income dataset with \emph{subgroup bias},
    for the binary classification task of predicting whether an individual earns $>$\$50,000 with a binary subgrouping based on \emph{gender}.
    \texttt{ERM (LD)} refers to a model based on ERM (empirical risk minimization),
    trained on a \emph{l}abelled \emph{d}eployment set; thus not suffering from bias in the training set.
    \textsc{Top left}: Accuracy.
    \textsc{Top right}: Positive rate ratio.
    \textsc{Bottom left}: True positive rate ratio.
    \textsc{Bottom right}: True negative rate ratio.
    For the \texttt{Ranking} clustering, the clustering accuracy was 69.7\% $\pm$ 0.3\%;
    for \texttt{K-means} it was 43\% $\pm$ 3\%.
    }%
    \label{fig:adult-subgroup-bias}
\end{figure*}
\begin{figure*}[p]
    \centering
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_acc.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_prr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_tprr.pdf}
    \includegraphics[width=\columnwidth]{figures/adult_miss_s_tnrr.pdf}
    \caption{%
    Results for the Adult Income dataset with a \emph{missing subgroup},
    for the binary classification task of predicting whether an individual earns $>$\$50,000 with a binary subgrouping based on \emph{gender}.
    \texttt{ERM (LD)} refers to a model based on ERM (empirical risk minimization),
    trained on a \emph{l}abelled \emph{d}eployment set; thus not suffering from bias in the training set.
    \textsc{Top left}: Accuracy.
    \textsc{Top right}: Positive rate ratio.
    \textsc{Bottom left}: True positive rate ratio.
    \textsc{Bottom right}: True negative rate ratio.
    For the \texttt{Ranking} clustering, the clustering accuracy was 60.4\% $\pm$ 0.8\%;
    for \texttt{K-means} it was 44\% $\pm$ 3\%.
    }%
    \label{fig:adult-missing-subgroup}
\end{figure*}
Figures~\ref{fig:adult-subgroup-bias} and \ref{fig:adult-missing-subgroup} show results from our method on the Adult Income dataset \cite{Dua:2017}.
This dataset is a common dataset for evaluating fair machine learning models. 
Each instance in the dataset is described by $14$ characteristics including gender, education, marital status, number of work hours per week among others, along with a label denoting income level ($\geq$\$50K or not). 
We transform the representation into $62$ real and binary features along with the subgroup label $s$. %%%%%%%%CHECK THESE VALUES%%%%%%%%%%%% 
The dataset is naturally imbalanced with respect to gender: 30\% of the males are labelled as earning more than \$50K per year (high income), while only 11\% of females are labelled as such.
For further details on the dataset construction, see section~\ref{ssec:dataset-construction-adult}.
%
Following standard practice in algorithmic fairness, e.g. \citet{zemel2013learning}, we consider gender to be the subgroup label $s$.

@@

\subsection{Visualizations of results}\label{sec:qual-results}
Figures~\ref{fig:attn_maps} and \ref{fig:cmnist-recon} show some additional visualizations for our results.
For details, see the captions.
\begin{figure*}[tb]
  \centering
    % \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=0.9\textwidth]{figures/celeba_attn_map.png}
    % \end{subfigure}
    % \hfill
    % \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=0.9\textwidth]{figures/cmnist_attn_map.png}
    % \end{subfigure}
  \caption{
    Example sample-wise attention maps for bags of CelebA (left) and Coloured MNIST (right) images sampled from a balanced deployment set. The training set is biased according to the SB setting where for CelebA ``smiling females'' constitute the missing source and for Colored MNIST {\color{purple}purple} fours constitute the missing source. The attention weights are used during the discriminator's aggregation step to compute a weighted sum over the bag. The attention-weight assigned to each sample is proportional to the lightness of its frame, with black signifying a weight of 0, white a weight of 1. Those samples belonging to the missing subgroup are assigned the highest weight as they signal from which dataset (training vs. deployment) the bag containing them was drawn from.
  }%
  \label{fig:attn_maps}
\end{figure*}

% \subsection{Qualitative results}\label{sec:qual-results}
\begin{figure*}[tb]
  \centering
  \begin{subfigure}[b]{0.39\textwidth}
    \centering
    \includegraphics[width=\textwidth]{example_images/fresh-dawn-2179_train_reconstructions_9900.png}
    \caption{
    Different reconstructions on the training set.
    Corresponding to: original, full reconstruction, reconstruction of $z_y$, reconstruction of $z_s$.
    }%
    \label{fig:cmnist-recon-training}
  \end{subfigure}
  % \hfill
  \quad
  \begin{subfigure}[b]{0.39\textwidth}
    \centering
    \includegraphics[width=\textwidth]{example_images/fresh-dawn-2179_context_reconstructions_9900.png}
    \caption{
    Different reconstructions on the deployment set.
    Corresponding to: original, full reconstruction, reconstruction of $z_y$, reconstruction of $z_s$.
    }%
    \label{fig:cmnist-recon-deployment}
  \end{subfigure}
  \caption{
   Visualization of our method's solutions for the Coloured MNIST dataset, with {\color{purple}purple} as the missing subgroup.
   In each of the subfigures \ref{fig:cmnist-recon-training} and \ref{fig:cmnist-recon-deployment}:
   Column 1 shows the original images from $x$ from the respective set.
   Column 2 shows plain reconstructions generated from $x_\textit{recon}=g(f_y(x), f_s(x))$.
   Column 3 shows reconstruction with zeroed-out $z_s$: $g(f_y(x), 0)$, which effectively visualises $z_y$.
   Column 4 shows the result of an analogous process where $z_y$ was zeroed out instead.
  }%
  \label{fig:cmnist-recon}
\end{figure*}
% Given a learned invariant representation, we can generate a reconstruction to visualise the information contained in it.
% An example of this can be seen in \figref{fig:3dig-examples}.
% This is from our experiment with 3 digits in Colored MNIST.
% We can clearly see that the reconstructed invariant representation has lost all color information;
% instead all digits are magenta-colored, which was the majority color in the training set.

@@

%   \includegraphics[width=\columnwidth]{figures/cmnist_2v4_partial_acc.pdf}
%   \includegraphics[width=\columnwidth]{figures/cmnist_2v4_partial_pr.pdf}
%   \includegraphics[width=\columnwidth]{figures/cmnist_2v4_partial_tpr.pdf}
%   \includegraphics[width=\columnwidth]{figures/cmnist_2v4_partial_tnr.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_partial_overcluster_acc.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_partial_overcluster_prr.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_partial_overcluster_tprr.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_partial_overcluster_tnrr.pdf}

@@

%   \includegraphics[width=\columnwidth]{figures/cmnist_2v4_miss_s_alt_acc.pdf}
%   \includegraphics[width=\columnwidth]{figures/cmnist_2v4_miss_s_alt_pr.pdf}
%   \includegraphics[width=\columnwidth]{figures/cmnist_2v4_miss_s_alt_tpr.pdf}
%   \includegraphics[width=\columnwidth]{figures/cmnist_2v4_miss_s_alt_tnr.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_acc.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_prr.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_tprr.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_2v4_miss_s_overcluster_tnrr.pdf}

@@

%   \includegraphics[width=\columnwidth]{figures/cmnist_3dig_4miss_hgr.pdf}\\
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_prr-min.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_prd-max.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_tprr-min.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_tprd-max.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_tnrr-min.pdf}
  \includegraphics[width=0.8\columnwidth]{figures/cmnist_3dig_4miss_tnrd-max.pdf}

@@

%   \includegraphics[width=\columnwidth]{figures/celeba_gender_smiling_acc.pdf}
%   \includegraphics[width=\columnwidth]{figures/celeba_gender_smiling_pr.pdf}
  \includegraphics[width=\columnwidth]{figures/celeba_gender_smiling_tprr.pdf}
  \includegraphics[width=\columnwidth]{figures/celeba_gender_smiling_tnrr.pdf}

>>>>

% \subsection{Why not use a fair clustering method?}
% Current fair clustering methods \citep{chierichetti2017fair, backurs2019scalable, huang2019coresets} cluster based on the protected attribute and thus are not applicable to our setting in which the deployment set is unlabelled and the training set is incomplete with respect to $s$.

% \begin{figure*}[t]
% \centering
% \includegraphics[width=0.6\textwidth,page=2]{paper3/figures/ideal.pdf}
% \caption{Overview of the zero-shot stratification problem. Training dataset (pairs of input data $x$ and class label $y$) will only contain data points that are labelled ``yes'' by the decision policy. This systematic bias might result in a subgroup(s) to have zero labelled data (in the example above, ``married'' subgroup has zero labelled data). The subgrouping information $s$ is unavailable/unlabelled at deployment time, and is only partially labelled at train time.}
% \label{fig:censoring}
% \end{figure*}

\section{Appendix}\label{sec:zsf-appendix}
\subsection{Results for Adult Income}\label{sec:adult-results}
\begin{figure*}[p]
    \centering
    \includegraphics[width=\columnwidth]{paper3/figures/adult_partial_acc.pdf}
    \includegraphics[width=\columnwidth]{paper3/figures/adult_partial_prr.pdf}
    \includegraphics[width=\columnwidth]{paper3/figures/adult_partial_tprr.pdf}
    \includegraphics[width=\columnwidth]{paper3/figures/adult_partial_tnrr.pdf}
    \caption{%
    Results for the Adult Income dataset with \emph{subgroup bias},
    for the binary classification task of predicting whether an individual earns $>$\$50,000 with a binary subgrouping based on \emph{gender}.
    \texttt{ERM (LD)} refers to a model based on ERM (empirical risk minimization),
    trained on a \emph{l}abelled \emph{d}eployment set; thus not suffering from bias in the training set.
    \textsc{Top left}: Accuracy.
    \textsc{Top right}: Positive rate ratio.
    \textsc{Bottom left}: True positive rate ratio.
    \textsc{Bottom right}: True negative rate ratio.
    For the \texttt{Ranking} clustering, the clustering accuracy was 69.7\% $\pm$ 0.3\%;
    for \texttt{K-means} it was 43\% $\pm$ 3\%.
    }%
    \label{fig:adult-subgroup-bias}
\end{figure*}
\begin{figure*}[p]
    \centering
    \includegraphics[width=\columnwidth]{paper3/figures/adult_miss_s_acc.pdf}
    \includegraphics[width=\columnwidth]{paper3/figures/adult_miss_s_prr.pdf}
    \includegraphics[width=\columnwidth]{paper3/figures/adult_miss_s_tprr.pdf}
    \includegraphics[width=\columnwidth]{paper3/figures/adult_miss_s_tnrr.pdf}
    \caption{%
    Results for the Adult Income dataset with a \emph{missing subgroup},
    for the binary classification task of predicting whether an individual earns $>$\$50,000 with a binary subgrouping based on \emph{gender}.
    \texttt{ERM (LD)} refers to a model based on ERM (empirical risk minimization),
    trained on a \emph{l}abelled \emph{d}eployment set; thus not suffering from bias in the training set.
    \textsc{Top left}: Accuracy.
    \textsc{Top right}: Positive rate ratio.
    \textsc{Bottom left}: True positive rate ratio.
    \textsc{Bottom right}: True negative rate ratio.
    For the \texttt{Ranking} clustering, the clustering accuracy was 60.4\% $\pm$ 0.8\%;
    for \texttt{K-means} it was 44\% $\pm$ 3\%.
    }%
    \label{fig:adult-missing-subgroup}
\end{figure*}
Figures~\ref{fig:adult-subgroup-bias} and \ref{fig:adult-missing-subgroup} show results from our method on the Adult Income dataset \cite{Dua:2017}.
This dataset is a common dataset for evaluating fair machine learning models. 
Each instance in the dataset is described by $14$ characteristics including gender, education, marital status, number of work hours per week among others, along with a label denoting income level ($\geq$\$50K or not). 
We transform the representation into $62$ real and binary features along with the subgroup label $s$. %%%%%%%%CHECK THESE VALUES%%%%%%%%%%%% 
The dataset is naturally imbalanced with respect to gender: 30\% of the males are labelled as earning more than \$50K per year (high income), while only 11\% of females are labelled as such.
For further details on the dataset construction, see section~\ref{ssec:dataset-construction-adult}.
%
Following standard practice in algorithmic fairness, e.g. \citet{zemel2013learning}, we consider gender to be the subgroup label $s$.

@@

\subsection{Visualizations of results}\label{sec:qual-results}
Figures~\ref{fig:attn_maps} and \ref{fig:cmnist-recon} show some additional visualizations for our results.
For details, see the captions.
\begin{figure*}[tb]
  \centering
    % \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=0.9\textwidth]{paper3/figures/celeba_attn_map.png}
    % \end{subfigure}
    % \hfill
    % \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=0.9\textwidth]{paper3/figures/cmnist_attn_map.png}
    % \end{subfigure}
  \caption{
    Example sample-wise attention maps for bags of CelebA (left) and Coloured MNIST (right) images sampled from a balanced deployment set. The training set is biased according to the SB setting where for CelebA ``smiling females'' constitute the missing source and for Coloured MNIST {\color{purple}purple} fours constitute the missing source. The attention weights are used during the discriminator's aggregation step to compute a weighted sum over the bag. The attention-weight assigned to each sample is proportional to the lightness of its frame, with black signifying a weight of 0, white a weight of 1. Those samples belonging to the missing subgroup are assigned the highest weight as they signal from which dataset (training vs. deployment) the bag containing them was drawn from.
  }%
  \label{fig:attn_maps}
\end{figure*}

% \subsection{Qualitative results}\label{sec:qual-results}
\begin{figure*}[tb]
  \centering
  \begin{subfigure}[b]{0.39\textwidth}
    \centering
    \includegraphics[width=\textwidth]{paper3/example_images/fresh-dawn-2179_train_reconstructions_9900.png}
    \caption{
    Different reconstructions on the training set.
    Corresponding to: original, full reconstruction, reconstruction of $z_y$, reconstruction of $z_s$.
    }%
    \label{fig:cmnist-recon-training}
  \end{subfigure}
  % \hfill
  \quad
  \begin{subfigure}[b]{0.39\textwidth}
    \centering
    \includegraphics[width=\textwidth]{paper3/example_images/fresh-dawn-2179_context_reconstructions_9900.png}
    \caption{
    Different reconstructions on the deployment set.
    Corresponding to: original, full reconstruction, reconstruction of $z_y$, reconstruction of $z_s$.
    }%
    \label{fig:cmnist-recon-deployment}
  \end{subfigure}
  \caption{
   Visualization of our method's solutions for the Coloured MNIST dataset, with {\color{purple}purple} as the missing subgroup.
   In each of the subfigures \ref{fig:cmnist-recon-training} and \ref{fig:cmnist-recon-deployment}:
   Column 1 shows the original images from $x$ from the respective set.
   Column 2 shows plain reconstructions generated from $x_\textit{recon}=g(f_y(x), f_s(x))$.
   Column 3 shows reconstruction with zeroed-out $z_s$: $g(f_y(x), 0)$, which effectively visualises $z_y$.
   Column 4 shows the result of an analogous process where $z_y$ was zeroed out instead.
  }%
  \label{fig:cmnist-recon}
\end{figure*}
% Given a learned invariant representation, we can generate a reconstruction to visualise the information contained in it.
% An example of this can be seen in \figref{fig:3dig-examples}.
% This is from our experiment with 3 digits in Coloured MNIST.
% We can clearly see that the reconstructed invariant representation has lost all colour information;
% instead all digits are magenta-coloured, which was the majority colour in the training set.

@@

%   \includegraphics[width=\columnwidth]{paper3/figures/cmnist_2v4_partial_acc.pdf}
%   \includegraphics[width=\columnwidth]{paper3/figures/cmnist_2v4_partial_pr.pdf}
%   \includegraphics[width=\columnwidth]{paper3/figures/cmnist_2v4_partial_tpr.pdf}
%   \includegraphics[width=\columnwidth]{paper3/figures/cmnist_2v4_partial_tnr.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_2v4_partial_overcluster_acc.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_2v4_partial_overcluster_prr.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_2v4_partial_overcluster_tprr.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_2v4_partial_overcluster_tnrr.pdf}

@@

%   \includegraphics[width=\columnwidth]{paper3/figures/cmnist_2v4_miss_s_alt_acc.pdf}
%   \includegraphics[width=\columnwidth]{paper3/figures/cmnist_2v4_miss_s_alt_pr.pdf}
%   \includegraphics[width=\columnwidth]{paper3/figures/cmnist_2v4_miss_s_alt_tpr.pdf}
%   \includegraphics[width=\columnwidth]{paper3/figures/cmnist_2v4_miss_s_alt_tnr.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_2v4_miss_s_overcluster_acc.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_2v4_miss_s_overcluster_prr.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_2v4_miss_s_overcluster_tprr.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_2v4_miss_s_overcluster_tnrr.pdf}

@@

%   \includegraphics[width=\columnwidth]{paper3/figures/cmnist_3dig_4miss_hgr.pdf}\\
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_3dig_4miss_prr-min.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_3dig_4miss_prd-max.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_3dig_4miss_tprr-min.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_3dig_4miss_tprd-max.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_3dig_4miss_tnrr-min.pdf}
  \includegraphics[width=0.8\columnwidth]{paper3/figures/cmnist_3dig_4miss_tnrd-max.pdf}

@@

%   \includegraphics[width=\columnwidth]{paper3/figures/celeba_gender_smiling_acc.pdf}
%   \includegraphics[width=\columnwidth]{paper3/figures/celeba_gender_smiling_pr.pdf}
  \includegraphics[width=\columnwidth]{paper3/figures/celeba_gender_smiling_tprr.pdf}
  \includegraphics[width=\columnwidth]{paper3/figures/celeba_gender_smiling_tnrr.pdf}
